ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-02 paper.tex
Mentioned VISAPP results. However, I have doubts that we should use it, it might only confuse the reader since the experiments differ completely

From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.

@@

\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
\todo{Make sure paper fits into 10+1 page limit for content and references}

>>>>

From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
These results compare favourably with those collected from experiments performed with this system's previous iteration where an average time to target of 31s was recorded~\cite{lock2019active}. 
However, it should be noted that the system implementation and experiment design for this work is significantly different and this comparison is symbolic more than it is indicative of major improvement.
\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}

@@

\todo{Make sure paper fits into 10+1 page limit for content and references}
